---
title: "Barriers and facilitators to sharing and reusing video research data"
subtitle: "Reproducible documentation of analyses"
author:
  - name: "[blinded]"
    email: ""
    affiliation: "[blinded]"
    correspondence: true
date: "`r Sys.Date()`" # inserts the date of compiling
editor: source
execute:
  echo: true
  warning: false
  message: false
  cache: false # true will prevent embed-resources
format: 
  html:
    theme: cerulean
    fontsize: 0.85em
    toc: true
    toc-location: left
    toc-depth: 4
    embed-resources: true # will make standalone html file
    code-fold: true
    code-tools: true
    code-link: true
editor_options: 
  chunk_output_type: console
---

# loading packages

```{r}
library(tidyverse)
library(rio)
library(xfun)
library(here)
library(kableExtra)
```

# Analyses in the Introduction section

## Frequency of data sharing in video studies

* The following __search query__ was applied in [Web of Science](https://www.webofscience.com) on September 6 2023: `("video study" OR "video data") AND (classroom OR teach*)` in "Topic" (Searches title, abstract, author keywords, and Keywords Plus).
* We have further narrowed the __publication years__ to 2000 - 2023, as digital archiving infrastructures were increasingly established from 2000 onwards.
  
::: {.callout-note appearance="minimal"}
## This resulted in 285 documents.
Click here to `r embed_file(here("3_data/1_Frequency_of_data_sharing_WoS_export.csv"), text="download the exported results")`.
:::

  
* __Inclusion criteria__ for subsequent screening of the results
  - The document describes an empirical study
  - The study uses video data to investigate an educational topic
  - The document describes primary research (does not reuse video data)
* __Exclusion criteria__
  - The document is a methods paper
  - The study reuses video data

Strategy of synthesis:

* Duplicates of research projects (several publications from one video data set) will be synthesized to one case. Within the case we will investigate each document.


```{r}
freq_screened <- rio::import(file=here("3_data/2_Frequency_of_data_sharing_screened_rayyan.csv")) # this is articles.csv (I renamed the file before)

freq_screened <- freq_screened %>%
  dplyr::mutate(excl_reason = str_extract(.$notes, "RAYYAN-EXCLUSION-REASONS:.*?(\\||$)"), # extract exclusion reasons
                labels = str_extract(.$notes, "RAYYAN-LABELS:.*?(\\||$)"),       # extract labels coded
                decision_c1 = str_extract(.$notes, "Jürgen\"\"=>\"\".*?\"\""),    # extract decision from coder 1 -> CHANGE NAME!
                decision_c2 = str_extract(.$notes, "Juergen\"\"=>\"\".*?\"\"")) %>% # extract decision from coder 2 -> CHANGE NAME!
  # remove prefixes or recode
  dplyr::mutate(excl_reason = str_remove_all(excl_reason, "RAYYAN-EXCLUSION-REASONS:\\s"),
                labels = str_remove_all(labels, "RAYYAN-LABELS:\\s|\\s\\|"),
                decision_c1 = case_when(                                      
                  str_detect(decision_c1, "Excluded") ~ "Excluded",           
                  str_detect(decision_c1, "Included") ~ "Included",           
                  str_detect(decision_c1, "Maybe") ~ "Maybe"),                
                decision_c2 = case_when(                                      
                  str_detect(decision_c2, "Excluded") ~ "Excluded",           
                  str_detect(decision_c2, "Included") ~ "Included",           
                  str_detect(decision_c2, "Maybe") ~ "Maybe"),
                agreement = case_when(        # is there agreement on the decision?
                  decision_c1 == decision_c2 ~ 1,
                  TRUE ~ 0)
  )



# crosstab of coding results
table(freq_screened$decision_c1, freq_screened$decision_c2)
table(freq_screened$decision_c1)
table(freq_screened$decision_c2)

# show documents with disagreeing decision
freq_screened |>
  dplyr::filter(agreement == 0) |>    # selecting the documents with disagreement 
  dplyr::select(authors, title, year) |> # which information should be displayed?
  kbl()

# write table with clean data set to data folder
rio::export(freq_screened, file = here("3_data/3_Frequency_of_data_sharing_screened_clean.csv"))
```
  
::: {.callout-note appearance="minimal"}
## This resulted in # documents.
Click here to `r embed_file(here("3_data/3_Frequency_of_data_sharing_screened_clean.csv"), text="download the screened results")`.
:::



  
We then coded: 

* Whether authors made a statement about the accessibility of the data
* Whether the openness include public access, restricted access, no access, access upon request
* Whether the authors use established infrastructure (repositories or research data centers)
* Whether the journal mandates authors to make a statement about the accessibility of the data


# R Version & Environment

```{r}
sessionInfo()
```